Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2023-11-10 manuscript/manuscript.Rmd
Added work on deriving maximum likelihood estimation.

---
title: "Shift-sensitive Power Transformations for Transforming Data to Normality"
author: "Alex Zwanenburg"
date: "2023-01-06"
output:
  pdf_document:
    latex_engine: lualatex
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{booktabs}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

>>>>

---
title: "Location and Scale-Invariant Power Transformations for Transforming Data to Normality"
author: "Alex Zwanenburg"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{booktabs}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---
